Class-based network segregation, Economic Inequality and Redistributive Preferences across societies

### 2024-04-15 paper1_jiturra.Rmd
udpate

dfreg <- df1 %>% dplyr::select(
  egal = egal2,
  dclass3res_V,
  dclass3spo_V,
  # homclass3_V_res,
  know_total,
  socialtrust,
  Q03pcm,
  edyears,
  female,
  agenum,
  religion,
  partner,
  union,
  workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  gdppercapita,
  country2, country, country3,
) %>%
  # filter(oecd == "OECD") %>%
  filter(country2 != "SVN") %>% 
  na.omit() %>% 
    mutate(loggdppercapita=scale(gdppercapita/1000),
         edyears2 = edyears ^ 2,
         age2 = agenum ^ 2, 
         # gini_disp=scale(gini_disp),
         )

@@

header <- list("Q1"=1:2,"Q2"=3:4,"Q3"=5:6,"Q4"=7:8,"Q5"=9:10)
texreg(digclas1_Q05,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,include.ci = FALSE,custom.header = header,
       caption = paste("(\\#tab:table1-groups)","Fixed effects linear regression models for Class-based network segregation and Redistributive Preferences by Income Inequality Quintiles"),
       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
       caption.above = T,leading.zero = T,
       custom.coef.map = ccoef,
       symbol = "+",scalebox = 0.60,
      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
      custom.gof.rows = list("Country FE"=rep("Yes",10)),
      # include.loglik = FALSE,include.aic = FALSE,
      # custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
       float.pos = "h!",
      # file = "table1.html"
       use.packages = F)
```

```{r fig1-marg-ineqgrup, fig.dim=c(10,5),fig.cap='Average Marginal Effects of Network homogeneity conditionated by Social class on Redistributive Preferences by Income Inequality Groups',warning=FALSE}
marginal <- bind_rows(
plot_slopes(digclas1_VW_Q1_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=1),
plot_slopes(digclas1_VW_Q2_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F)  %>% mutate(quintile=2),
plot_slopes(digclas1_VW_Q03_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=3),
plot_slopes(digclas1_VW_Q04_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=4),
plot_slopes(digclas1_VW_Q05_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=5))
marginal$quintile <- factor(marginal$quintile,labels = c("Q1","Q2","Q3","Q4","Q5"))

ggplot(data=marginal,aes(x = dclass3res_V, y = estimate,ymin= conf.low, ymax=conf.high)) +
  geom_point(size=2) + 
  geom_errorbar(width=.2)+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0,color="red") +
  facet_grid(~quintile) +
  labs(x=NULL,y="Redistributive preferences")  
```

>>>>

dfreg <- df1 %>% dplyr::select(
  egal = egal2,
  dclass3res_V,
  dclass3spo_V,
  homclass3_V_res,
  know_total,
  socialtrust,
  Q03pcm,
  edyears,
  female,
  agenum,
  religion,
  partner,
  union,
  workst,
  WEIGHT,
  region,
  "gini_disp"=wid_gini_disp,
  d10d1=wid_p90p10,
  wid_p90p50,
  top10=wid_sharetop10,
  gdppercapita,
  country2, country, country3,
) %>%
  # filter(oecd == "OECD") %>%
  filter(country2 != "SVN") %>% 
  na.omit() %>% 
    mutate(loggdppercapita=scale(gdppercapita/1000),
         edyears2 = edyears ^ 2,
         age2 = agenum ^ 2, 
         # gini_disp=scale(gini_disp),
         )

@@

header <- list("Q1"=1:2,"Q2"=3:4,"Q3"=5:6,"Q4"=7:8,"Q5"=9:10)
texreg(digclas1_Q05,stars = c(0.001, 0.01, 0.05, 0.1),single.row = F,include.ci = FALSE,custom.header = header,
       caption = paste("(\\#tab:table1-groups)","Fixed effects linear regression models for Class-based network segregation and Redistributive Preferences by Income Inequality Quintiles"),
       custom.note = "Note: Models include sampling weights. Gender, age, marital status and religion are included as controls. Standard errors in parentheses. %stars",
       caption.above = T,leading.zero = T,
       custom.coef.map = ccoef,
       symbol = "+",scalebox = 0.55,
      groups = list("Social Class (Ref.= Service Class)" = 4:5, "Household Income (Ref.= Tertile I)"= 7:9,  "Partner's Social Class (Ref.= Service Class)" = 12:14, "Homogeneity x Social Class"=15:16),
      custom.gof.rows = list("Country FE"=rep("Yes",10)),
      # include.loglik = FALSE,include.aic = FALSE,
      # custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
       float.pos = "h!",
      # file = "table1.html"
       use.packages = F)
```

```{r fig1-marg-ineqgrup, fig.dim=c(15,5),fig.cap='Average Marginal Effects of Network homogeneity conditionated by Social class on Redistributive Preferences by Income Inequality Groups',warning=FALSE}
marginal <- bind_rows(
plot_slopes(digclas1_VW_Q1_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=1),
plot_slopes(digclas1_VW_Q2_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F)  %>% mutate(quintile=2),
plot_slopes(digclas1_VW_Q03_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=3),
plot_slopes(digclas1_VW_Q04_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=4),
plot_slopes(digclas1_VW_Q05_2, variables = "homclass3_V_res", by = "dclass3res_V",draw = F) %>% mutate(quintile=5))
marginal$quintile <- factor(marginal$quintile,labels = c("Gini (Q1)","Gini Q2","Gini Q3","Gini Q4","Gini Q5"))
marginal$dclass3res_V <- forcats::fct_rev(marginal$dclass3res_V)

ggplot(data=marginal,aes(x = dclass3res_V, y = estimate,ymin= conf.low, ymax=conf.high)) +
  geom_point(size=2) + 
  geom_errorbar(width=.2)+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0,color="red") +
  facet_grid(~quintile) +
  labs(x=NULL,y="Redistributive preferences"
       # title = "Average Marginal Effects for Class-based network segregation on Redistributive preferences by Social Class and Income Inequality groups"
       )
